Autonomous Oceanographic Data Collection using Excursion Sets of Vector-valued Gaussian Random Fields

### 2020-06-20 section3_archive_June19.tex
before running through from start.

This strategy does not account for the uncertainty in the GP
variables, \textcolor{red}{(C.T.: do we need this sentence? does it mean anything?) but is instead applicable only if one design (node) has EPs
closer to $0.5$ (see Table \ref{tab:sim_rhoab}, row
two).}

Additionally, this strategy does not account for spatial
correlation. This strategy lacks memory of where it has been and where
the uncertainty has been reduced, and therefore susceptible to local
minima.

@@

Based on the currently available data the myopic strategy selects the location that leads to the biggest expected reduction in IBV:
\begin{criterion}[Myopic]
\begin{equation}\label{critSEQ}
    \spatloc_{\stage + 1} = \argmin_{\spatloc \in \candidates} \EIBV_{\stage}\left(\spatloc\right)
\end{equation}
\end{criterion}

@@

  \begin{criterion}[2-steps lookahead]
      The next observation location $\spatloc_{\stage + 1}$ is selected according to
      \begin{align}\label{critLA}
          \spatloc_{\stage + 1} = \argmin_{\spatloc \in \candidates}~ \mathbb{E}_{\stage}\left[\min_{\spatloc' \in
                  \candidates(\spatloc)} \EIBV_{\stage}\left(\spatloc' ; \spatloc,
      Y\right)\right]
      \end{align}
  where $Y$ is a random variable distributed according to the conditional
  law of $\gp_{\spatloc}$ at step $\stage$ (note it silently depends on the considered point
  $\spatloc$). Here, the dependence of the set of candidates on the current location has been made explicit for the second stage of measurements.
  \end{criterion}

>>>>

%This strategy does not account for the uncertainty in the GP variables, \textcolor{red}{(C.T.: do we need this sentence? does it mean anything?) but is instead applicable only if one design (node) has EPs closer to $0.5$ (see Table \ref{tab:sim_rhoab}, row two).}

%Additionally, this strategy does not account for spatial correlation. This strategy lacks memory of where it has been and where the uncertainty has been reduced, and therefore susceptible to local minima.

@@

Based on the currently available data the myopic strategy selects the location that leads to the biggest expected reduction in IBV:
\begin{criterion}[Myopic]
The next observation location $\spatloc_{\stage + 1}$ is chosen among the minimizers in $\candidates$ of the criterion:
\begin{equation}\label{critSEQ}
     C_{\text{myopic}}(u) = \EIBV_{\stage}\left(\spatloc\right)
\end{equation}
\end{criterion}

@@

  \begin{criterion}[2-steps lookahead]
      The next observation location $\spatloc_{\stage + 1}$ is chosen among the minimizers in $\candidates$ of the criterion
      \begin{align}\label{critLA}
          C_{\text{2-steps}}(u) &= \mathbb{E}_{\stage}\left[\min_{\spatloc' \in
                  \candidates(\spatloc)} \EIBV_{\stage}\left(\spatloc' ; \spatloc,
      Y\right)\right]
      \end{align}
  where $Y$ is a random variable distributed according to the conditional
  law of $\gp_{\spatloc}$ at step $\stage$ (note it silently depends on the considered point
  $\spatloc$). Here, the dependence of the set of candidates on the current location has been made explicit for the second stage of measurements.
  \end{criterion}
